---
title: "2-bn_analysis"
author: "Bernard"
date: "2020-09-08"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

This is an example of a Bayesian network, with directed arcs. I only perform the analysis on a subset of provided variables.

### Import libraries

```{r, message=F, warning=F}

rm (list = ls())
# Helper
library (tidyverse)

# BN
library (bnlearn)

# Model
library (caret)

# Feature parallel
library (doParallel)

# Plot
library (Rgraphviz)

```

### Import data
```{r}

dat <- readRDS ("output/dat.RDS")

```

### Collapse variables

```{r}
dat <- dat %>%
  mutate (ppt_medn_base = (ppt_medn_aff_base + ppt_medn_naff_base)/2,
          ppt_uln_base = (ppt_uln_aff_base + ppt_uln_naff_base)/2,
          ppt_radn_base = (ppt_radn_aff_base + ppt_radn_naff_base)/2,
          ppt_neck_base = (ppt_neck_aff_base + ppt_neck_naff_base)/2,
          ppt_cts_base = (ppt_cts_aff_base + ppt_cts_naff_base)/2,
          ppt_ta_base = (ppt_ta_aff_base + ppt_ta_naff_base)/2) %>%
  select (-c(ppt_medn_aff_base:ppt_ta_naff_base))
```


### BN analysis

#### Create blacklist

```{r}

var.excl <- c(grep ("groc", names (dat), value = TRUE) ,
              grep ("worst", names (dat), value = TRUE) ,
              grep ("base", names (dat), value = TRUE) ,
              "age", "pain_years", "pain_extent", "aff_side", "emg")
df.bn = as.data.frame (dat)[, !names (dat) %in% var.excl] %>%
  na.omit()

df.bn$grp <- factor (df.bn$grp)

rx.var <- "grp"
demo.var = grep("age|sex|years|emg", colnames (df.bn), value = TRUE)
base.var = grep("_base", colnames (df.bn), value = TRUE)
mth1.var = grep("_1", colnames (df.bn), value = TRUE)
mth3.var = grep("_3", colnames (df.bn), value = TRUE)
mth6.var = grep("_6", colnames (df.bn), value = TRUE)
outcome.var = grep("_12", colnames (df.bn), value = TRUE)

pair_var <- expand.grid(from = names (df.bn),
                        to = names (df.bn)) %>%
  rownames_to_column()

tiers_keep <- pair_var %>%
  filter (!(grepl (paste0(outcome.var, collapse = "|"),from))) %>%
  filter (!(grepl (paste0(rx.var, collapse = "|"),to))) %>%
  filter (!(grepl (paste0(mth6.var, collapse = "|"), from) & 
              grepl (paste0(c(demo.var, base.var, mth1.var, mth3.var), collapse = "|"),to))) %>%
  filter (!(grepl (paste0(mth3.var, collapse = "|"), from) & 
              grepl (paste0(c(demo.var, base.var, mth1.var), collapse = "|"),to))) #%>%
  # filter (!(grepl (paste0(mth1.var, collapse = "|"), from) & 
  #           grepl (paste0(c(demo.var, base.var), collapse = "|"),to))) %>%
  # filter (!(grepl (paste0(base.var, collapse = "|"), from) & 
  #         grepl (paste0(c(demo.var), collapse = "|"),to)))

bl <- anti_join(pair_var, tiers_keep, by = "rowname")  %>%
  filter (from != to) %>%
  select (from, to)


```


#### Build the final model using model averaging

```{r}

boot <- boot.strength(df.bn,
                      R = 200,
                      algorithm = "hc",
                      algorithm.args = list (blacklist = bl))

  

```

#### Get averaged model

```{r}

avg <-  averaged.network(boot, threshold = 0.5)
fit <-  bn.fit (avg, df.bn, method = "mle")
g <- strength.plot(avg, boot, shape = "ellipse")
graph::nodeRenderInfo(g) = list(fontsize=18)
Rgraphviz::renderGraph(g)
```

#### Performance evaluation using nested cross validation. 
Not run yet.

Inner is bootstrap resampling for model averaging. 
Outer is bootstrap resampling k = 25 for performance evaluation.

```{r, eval= FALSE}

set.seed (2564)

flds <- createFolds(1:nrow(df.bn), 
                            k = 10, returnTrain = TRUE)
n_boot = 200
doParallel::registerDoParallel(7)

corr.df.list <- list()

for (k in seq_along(flds)) {
  
  train <-  df.bn [flds[[k]], ] %>% as.data.frame()
  test <- df.bn [-flds[[k]], ] %>% as.data.frame()
  
  doParallel::registerDoParallel(7)
  ############
  
  boot  =  foreach (B = 1: n_boot) %dopar%{
      boot.sample = train[sample(nrow(train), 
                                            nrow(train), replace = TRUE), ]
      bnlearn::structural.em(boot.sample, impute = "bayes-lw", max.iter = 5,
                                maximize.args = list(blacklist = bl,  
                                                      k = log(nrow(boot.sample))))
  }
  #############
  stopImplicitCluster()
  
  bootstr <-  custom.strength(boot, nodes = names(train))
  avg <-  averaged.network(bootstr, threshold = 0.7)
  fit <-  bn.fit (avg, train, method = "mle")
  
  imp.list = impute (fit, data = test, method = "bayes-lw")
  inames = names (imp.list) [-c(1:2)]
  corr.df =  structure(numeric(length (inames)), names = inames)
  
  for (var in inames) {
      corr.df[var] = cor(predict(fit, data = imp.list, var, method = "bayes-lw"), 
                         imp.list[, var])
    }
  
  corr.df.list[[k]] <- corr.df
  

}

corr.df <- bind_cols (corr.df.list) %>%
  apply (1, mean)

names (corr.df) <- inames

corr.df
```

# Save data

```{r, eval= FALSE}

save(avg, 
     bl, 
     demo.var,
     mth3.var,
     mth6.var,
     outcome.var,
     boot, 
     bootstr, 
     corr.df, 
     corr.df.list, 
     df.bn, 
     fit,
     file = "output/bn_data.RData")

```




