---
title: "3-network"
author: "bernard-liew"
date: "2020-09-24"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Load package

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse,
               qgraph,
               stats,
               bootnet,
               igraph,
               mgm,
               NetworkComparisonTest,
               rio,
               furrr,
               cowplot,
               huge,
               EGAnet)
```

## Clean data

### Import data
```{r}

dat <- readRDS ("output/dat.RDS")

```

### Collapse variables

```{r}
dat <- dat %>%
  mutate (ppt_medn_base = (ppt_medn_aff_base + ppt_medn_naff_base)/2,
          ppt_uln_base = (ppt_uln_aff_base + ppt_uln_naff_base)/2,
          ppt_radn_base = (ppt_radn_aff_base + ppt_radn_naff_base)/2,
          ppt_neck_base = (ppt_neck_aff_base + ppt_neck_naff_base)/2,
          ppt_cts_base = (ppt_cts_aff_base + ppt_cts_naff_base)/2,
          ppt_ta_base = (ppt_ta_aff_base + ppt_ta_naff_base)/2) %>%
  select (-c(ppt_medn_aff_base:ppt_ta_naff_base))
```

# Get baseline variables

```{r}
dat_base <- dat[, grepl ("base", names (dat))] %>%
  select (-worst_pain_base) %>%
  rename (func = cts_func_base,
          severity = cts_severe_base)
names (dat_base) <- str_remove_all (names(dat_base), "_base|ppt_|mean_")

dat_base

dat_base %>%
  pivot_longer(cols = everything (),
               names_to = "var",
               values_to = "val") %>%
  ggplot () +
  geom_histogram (aes (val)) +
  facet_wrap (~ var, ncol = 5, scales = "free_x")
```

# Get pain, cts

```{r}
dat_pain <- dat[, grepl ("func|severe|mean|grp|emg", names (dat))]
names (dat_pain) <- str_remove_all (names(dat_pain), "_base|cts_|mean_")
dat_pain$grp <- factor (dat_pain$grp)

dat_base %>%
  pivot_longer(cols = everything (),
               names_to = "var",
               values_to = "val") %>%
  ggplot () +
  geom_histogram (aes (val)) +
  facet_wrap (~ var, ncol = 5, scales = "free_x")
```

## Network analysis

### On baseline data

```{r}

stats_type <- c("edge", "strength", "betweenness", "expectedInfluence", "closeness")

df <- dat_base
df[, map_lgl (df, is.numeric)] <- huge.npn (df[, map_lgl (df, is.numeric)])
df <- map_df (df, as.numeric)
n_var <- ncol (df)

nw <- estimateNetwork(df, 
                    default="EBICglasso",
                    corMethod = "cor",
                    tuning = 0.5,
                    lambda.min.ratio = 0.001,
                    corArgs =
                      list(method = "pearson",
                           use = "pairwise.complete.obs"))


centr <- centralityTable(nw)
# 
# centr_stb <- bootnet(nw, 
#                      default="EBICglasso",
#                      corMethod = "cor",
#                       tuning = 0.5,
#                       lambda.min.ratio = 0.001,
#                       nBoots = 1000,
#                       type = "case",
#                       statistics = stats_type,
#                       corArgs =
#                         list(method = "pearson",
#                              use = "pairwise.complete.obs"))
# 
# cor_stb <-  corStability (centr_stb)
# 
# edgewts <- bootnet(nw, 
#                    default="EBICglasso",
#                     corMethod = "cor",
#                     tuning = 0.5,
#                     lambda.min.ratio = 0.001,
#                     nBoots = 1000,
#                     statistics = stats_type,
#                     corArgs =
#                       list(method = "pearson",
#                            use = "pairwise.complete.obs"))
# 
# mgm_fit <-  mgm (df,
#                 type= rep('g', 10),
#                 level=rep(1,10))
# 
#                
# pred <-  predict(mgm_fit, df)

```

#### Plot network

Arcs in blue means a positive correlation between connecting variables.

Arcs in red means a netative correlation between connecting variables.

Thickness of arcs gives you a qualitative indication of correlation magnitude.

```{r}
plot (nw)
```

#### Plot centrality

Degree centrality is defined as the number of connections incident to the node of interest.

Degree can be straightforwardly generalized to weighted networks by considering the sum of the weights of the connections (in absolute value), instead of their number. This generalization is called strength.

Closeness centrality is defined as the inverse of the sum of the distances of the focal node from all the other nodes in the network.

Betweenness centrality is defined as the number of the geodesics between any two nodes that pass through the focal one.

The greater the value of centrality indices to one, the more important the variable.

```{r}
centralityPlot(nw, scale = "relative")

# plot (centr_stb, statistics = c("closeness", "strength", "betweenness"))
# cor_stb
# plot (edgewts)
# cor_stb
```

### On pain data

```{r}

df <- dat_pain
df[, map_lgl (df, is.numeric)] <- huge.npn (df[, map_lgl (df, is.numeric)])
df <- map_df (df, as.numeric)
n_var <- ncol (df)

nw <- estimateNetwork(df, 
                    default="EBICglasso",
                    corMethod = "cor",
                    tuning = 0.5,
                    lambda.min.ratio = 0.001,
                    corArgs =
                      list(method = "pearson",
                           use = "pairwise.complete.obs"))


centr <- centralityTable(nw)
# 
# centr_stb <- bootnet(nw, 
#                      default="EBICglasso",
#                      corMethod = "cor",
#                       tuning = 0.5,
#                       lambda.min.ratio = 0.001,
#                       nBoots = 1000,
#                       type = "case",
#                       statistics = stats_type,
#                       corArgs =
#                         list(method = "pearson",
#                              use = "pairwise.complete.obs"))
# 
# cor_stb <-  corStability (centr_stb)
# 
# edgewts <- bootnet(nw, 
#                    default="EBICglasso",
#                     corMethod = "cor",
#                     tuning = 0.5,
#                     lambda.min.ratio = 0.001,
#                     nBoots = 1000,
#                     statistics = stats_type,
#                     corArgs =
#                       list(method = "pearson",
#                            use = "pairwise.complete.obs"))
# 
# mgm_fit <-  mgm (df,
#                 type= rep('g', 10),
#                 level=rep(1,10))
# 
#                
# pred <-  predict(mgm_fit, df)

```

#### Plot network

Arcs in blue means a positive correlation between connecting variables.

Arcs in red means a netative correlation between connecting variables.

Thickness of arcs gives you a qualitative indication of correlation magnitude.

```{r}
plot (nw)
```

#### Plot centrality

Degree centrality is defined as the number of connections incident to the node of interest.

Degree can be straightforwardly generalized to weighted networks by considering the sum of the weights of the connections (in absolute value), instead of their number. This generalization is called strength.

Closeness centrality is defined as the inverse of the sum of the distances of the focal node from all the other nodes in the network.

Betweenness centrality is defined as the number of the geodesics between any two nodes that pass through the focal one.

The greater the value of centrality indices to one, the more important the variable.

```{r}
centralityPlot(nw, scale = "relative")

# plot (centr_stb, statistics = c("closeness", "strength", "betweenness"))
# cor_stb
# plot (edgewts)
# cor_stb
```


