---
title: "4-TTH"
author: "bernard-liew"
date: "2021-06-23"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Load package

```{r, message=F, warning=F}

rm (list = ls())
# Helper
library (tidyverse)
library (skimr)
library (flextable)
library (officer)
library (arsenal)
library (kableExtra)
library (mice)
library (rstatix)

# Parallel
library (doParallel)

# BN
library (bnlearn)
library (Rgraphviz)

#SEM
library (lavaan)
library (semPlot)
library (semptools)
library (semTools)
library (SEMsens)
```

# Load data

```{r}
df <- rio::import("data/Tension Type Headache Database.sav")
res <- readRDS("output/res2.RDS")
list2env(res,globalenv())
#skim (df)
```


# Tidy data

https://psu-psychology.github.io/psy-597-SEM/09_model_comparison/model_comparison.html

```{r}

names (df) <- tolower (names(df))

df <- map_df(df, function(x) {attributes(x) <- NULL;x})

# Remove high missing
df <- df %>% 
  purrr::discard(~sum(is.na(.x))/length(.x)* 100 >=40)

rm_vars <- c("trpsactive",
             "trpslatent",
             "general_health",
             "vitality",
             "social_function",
             "emorional_role",
             "mental_health",
             "physical_function",
             "phyusical_role",
             "bodily_pain",
             grep ("udp", names (df), value = TRUE))
  
df2 <- df %>%
  mutate (ppt_cx = (udp_c5c6_right + udp_c5c6_left)/2,
          ppt_hx = (udp_temporal_right + udp_temporal_left)/2,
          ppt_rm = (udp_iimeta_right + udp_iimeta_left + udp_tibial_right + udp_tibial_left )/4) %>%
  dplyr::select (-all_of (rm_vars )) 

new_names <- c("Sex",
               "Age",
               "YearsP",
               "HInten",
               "HDura",
               "HFreq",
               "TrPs",
               "HDI_E",
               "HDI_P",
               "Sleep",
               "Dep",
               "Anx",
               "PPTcx",
               "PPThx",
               "PPTrm")

names (df2) <- new_names

df2$Sex <- factor (df2$Sex)
#df2$sex <- df2$sex -1
```

```{r, eval = FALSE, include = FALSE}

png ("../manuscript_tth/sm_fig1.png", height = 8, width = 15, units = "in", res = 100)
DataExplorer::plot_missing (df2) + 
  cowplot::theme_cowplot()
dev.off()
```

# Descriptives

```{r}

meanNsd_transform <- function (x) {

  m <- round (x[[1]][1], 2)
  s <- round (x[[1]][2], 2)

  m_s <- paste0(m, "(", s, ")")

  return (m_s)
}

tab1 <- tableby ( ~. , data = df2, digits = 2, digits.p = 2) %>%
  as.data.frame() %>%
  filter (!term %in% c("Nmiss", "range")) %>%
  select (-c(group.term:term, variable.type, Total)) 


tab2 <-  tab1[-c (1, seq (4, 34, 2)),]
tab2$label <- c("Sex-Male", "Sex-Female", "Age(years)", "Years with headache", 
                "Headache intensity", "Headache duration (hrs)", "Headache frequency",
                "Trigger points", "HDI-emotion", "HDI- physical", 
                "Sleep", "Depressive symptoms", "Anxiety symptoms",
                "PPT-cervical", "PPT-head", "PPT-remote")

for(row in 1:nrow(tab2)) {
    tab2[row, 2] <- meanNsd_transform (tab2[row, 2])
  }


colnames (tab2) <- c ("Variables", 
                      "Summary value")

# my_path <- paste0("../manuscript_tth/table_2", 
#                   "baseline",
#                   ".docx")
# 
# ft <- flextable(tab2) %>%
#   set_caption(caption = " Table 2.Baseline descriptive characteristics of cohort") %>%
#   autofit() 
# 
# my_doc <- read_docx()  %>% 
#   body_add_flextable(ft)
# 
# print (my_doc, target = my_path)
```

```{r}
tab2 %>%
  kbl() %>%
  kable_styling()
```


# Impute

```{r, eval = FALSE}
dat_imp <- mice::mice(df2, m = 20, seed = 155, maxit = 30, meth = "rf")

plot (dat_imp)

df3 <- mice::complete(dat_imp, "all") %>%
  map( ~ .x %>%
         mutate_if (is.numeric, scale, center = TRUE, scale = TRUE) %>%
         mutate (Sex = as.numeric (Sex) - 1))
```

# Correlations

```{r}
c <- cor(df3[[1]][,-1], method = "pearson", use = "complete.obs")
corrplot::corrplot(c, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```

# Measurement model using CFA

## Model

```{r, eval = FALSE, include = FALSE}
## Latent variable
cfa_form0 <- "
  # Latent
  Sensitivity =~ PPTcx + PPThx + PPTrm 
  Severity =~ HDura + HFreq + HInten
  Disability =~  HDI_P + HDI_E
  Distress =~ Dep + Anx
  
  # HInten~~Anx
  # PPThx~~HInten
  # PPTcx~~HDura
  # PPTcx~~HInten
"

cfa0_dummy <- cfa (cfa_form0, 
                   data = df3[[1]], 
                   std.lv = FALSE, 
                   auto.fix.first = TRUE, 
                   estimator = "MLR",
                   se = "robust.huber.white")
p0 <- semPlotModel(cfa0_dummy )

cfa0 <- cfa.mi (cfa_form0, 
             data = df3, 
             std.lv = FALSE, 
             auto.fix.first = TRUE, 
             estimator = "MLR",
             se = "robust.huber.white")

summary (cfa0)

res1 <- residuals(cfa0, type = "cor")$cov %>% 
  cor_gather() %>%
  mutate (form = paste0(var1, "~~", var2))  %>%
  filter (abs(cor) > 0.10) %>%
  arrange (abs(cor))

round (fitMeasures(cfa0, 
            #fit.measures = c("rmsea", "pvalue", "cfi", "tli", "srmr", "nnfi"), 
            test = "D2" , 
            pool.robust = TRUE)[c("rmsea", "pvalue", "cfi", "tli", "srmr", "nnfi")],3)
```

## Plot

```{r, eval = FALSE}

cfa0_dummy <- cfa (cfa_form0, 
                   data = df3[[1]], 
                   std.lv = FALSE, 
                   auto.fix.first = TRUE, 
                   estimator = "MLR",
                   se = "robust.huber.white")

fig <- semPlotModel(cfa0_dummy)

x = data.frame (summary (cfa0, standardized = TRUE))
fig@Pars$est <- x$est


png ("../manuscript_tth/fig1.png", height = 10, width = 15, units = "in", res = 100)
semPaths (fig, 
          what = "path", 
          whatLabels= "est",
          curve = TRUE,
          curvature = 2,
          residuals = FALSE,
          nCharNodes = 0,
          intercept = TRUE,
          edge.label.cex = 0.8,
          #exoCov = FALSE,
          color = list (lat = "grey", man = "white"),
          edge.label.position = 0.5,
          edge.color = "black")

dev.off()

```

```{r}
semPaths (fig, 
          what = "path", 
          whatLabels= "est",
          curve = TRUE,
          curvature = 2,
          residuals = FALSE,
          nCharNodes = 0,
          intercept = TRUE,
          edge.label.cex = 0.8,
          #exoCov = FALSE,
          color = list (lat = "grey", man = "white"),
          edge.label.position = 0.5,
          edge.color = "black")

```

## Bootstrap

```{r}
l2 = c(LETTERS, sort(do.call("paste0", expand.grid(LETTERS, LETTERS))))
```


# Theoretical model

```{r, eval = FALSE, include = FALSE}
## Latent variable
sem_form0 <- "
  # Latent
  Sensitivity =~ PPTcx + PPThx + PPTrm 
  Severity =~ HDura + HFreq + HInten
  Disability =~ HDI_E + HDI_P
  Distress =~ Dep + Anx

  # paths
  Distress ~ YearsP + Sex
  TrPs ~ YearsP + Sex
  Sensitivity ~ TrPs + Distress
  Severity ~ Sensitivity + Age 
  Sleep ~ Severity
  Disability ~ Severity + Sleep
  
  # HInten~~Anx
  # PPThx~~HInten
  # PPTcx~~HDura
  # PPTcx~~HInten
  
"


m0 <- sem.mi (sem_form0, 
           data = df3, 
           orthogonal = TRUE, 
           std.lv = FALSE, 
           auto.fix.first = TRUE, 
           estimator = "MLR",
           se = "robust.huber.white")

round (fitMeasures(m0, 
            test = "D2" , 
            pool.robust = TRUE)[c("rmsea", "pvalue", "cfi", "tli", "srmr", "nnfi")],3)
```


## Plot

```{r}

m0_dummy <- sem (sem_form0, 
                   data = df3[[1]], 
                   std.lv = FALSE, 
                   auto.fix.first = TRUE, 
                   estimator = "MLR",
                   se = "robust.huber.white")

fig <- semPlotModel(m0_dummy )

x = data.frame (summary (m0))
fig@Pars$est <- x$est

fig2 <- drop_nodes(fig, c("HDI_P", "HDI_E", "PPTcx", "PPThx", "PPTrm", "HDura", "HFreq", "HInten", "Dep", "Anx"))

fig2 <- semPaths (fig2, 
          what = "path", 
          whatLabels= "est",
          fixedStyle = c( "white","0"),
          freeStyle = c( "black","1"),
          residuals = FALSE,
          nCharNodes = 0,
          curveAdjacent = c("cov", "reg"),
          intercept = TRUE,
          edge.label.cex = 0.8,
          exoCov = FALSE,
          color = list (lat = "grey", man = "white"),
          edge.label.position = 0.5)

indicator_order  <- c("Sensitivity", "Severity", "Disability", "Distress",
                      "Age", "Sex", "YearsP", "Sleep", "TrPs")

indicator_factor <- c("Sensitivity", "Severity", "Disability", "Distress",
                      "Age", "Sex", "YearsP", "Sleep", "TrPs")

factor_layout <- matrix(c(NA, "Sex",NA,"Sensitivity", NA,  NA, NA,
                          NA, NA, NA,NA, NA, NA,NA,
                          NA, NA, NA,NA, NA, NA,NA,
                          "YearsP", NA,NA,NA,"Distress",NA,   NA,  
                          NA, NA, NA,NA, NA, NA,NA,
                          NA, NA, NA,NA, NA, NA,NA,
                          NA, NA, "Severity", NA,"Disability", NA,NA,
                          NA, NA, NA,NA, NA, NA,NA,
                          NA, NA, NA,NA, NA, NA,NA,
                          "TrPs", NA, "Age",NA, "Sleep", NA, NA),
                          byrow = TRUE, 10, 7)

factor_point_to <-  matrix(c(NA, "left",NA,"left",NA,    NA, NA,
                             NA, NA, NA,NA, NA, NA,NA,
                             NA, NA, NA,NA, NA, NA,NA,
                             "left", NA, NA, NA,"left",NA, NA,  
                             NA, NA, NA,NA, NA,NA, NA,
                             NA, NA, NA,NA, NA, NA,NA,
                             NA, NA, "left",NA, "left", NA,NA,
                             NA, NA, NA,NA, NA, NA,NA,
                             NA, NA, NA,NA, NA, NA,NA,
                             "left", NA, "left",NA, "left", NA, NA),
                          byrow = TRUE, 10, 7)

fig_mod <- set_sem_layout(fig2, 
                     indicator_order = indicator_order,
                     indicator_factor = indicator_factor,
                     factor_layout = factor_layout,
                     factor_point_to = factor_point_to)
plot(fig_mod)

```

## Montecarlo bootstrap coefficients

```{r}

params <- l2[1: length (coef(m0 ))]

paths <- coef(m0, standardized = TRUE)
names(paths) <- params
var_mat <- vcov(m0)
colnames(var_mat) <- rownames(var_mat) <- params

m0_coef <- monteCarloCI(expr = params,
                           ACM = var_mat,
                           coefs = paths)
m0_coef$paths <- names(coef(m0))

m0_coef <- m0_coef %>%
  filter (!grepl ("~~", paths)) %>%
  separate(paths, into = c("DV", "IV"), sep = "~|=~")
```

## Report

```{r, eval = FALSE}

fixed <- data.frame (DV = c("Sensitivity", "Severity", "Disability", "Distress"),
                     IV = c("PPTcx", "HDura", "HDI_P", "Dep"),
                     Coef = 1,
                     SE = NA,
                     `LB` = NA,
                     `UB` = NA,
                     Pval = NA,
                     Sig = NA)

# Export lavaan table
param_ex<- summary (m0, standardized = TRUE) %>%
  filter (op != "~~") %>%
  rename (DV = lhs,
          IV = rhs,
          Coef = est,
          SE = se,
          Pval = pvalue) %>%
  data.frame () %>%
  inner_join(m0_coef, by = c("DV", "IV")) %>%
  rename (`LB` = ci.lower,
          `UB` = ci.upper) %>%
  mutate_if (is.numeric, round, 3) %>%
  mutate (Sig = ifelse (Pval < 0.05/2, "s", "ns")) %>%
  dplyr::select ( DV, IV, Coef, SE, `LB`, `UB`,Pval, Sig) %>%
  mutate (Coef = as.numeric (Coef))%>%
  bind_rows (fixed)%>%
  mutate (type = ifelse (IV %in% c("PPTcx", "PPThx", "PPTrm", "HDura", "HFreq", "HInten",
                                   "Dep", "Anx", "HDI_P", "HDI_E"), "LV", "Reg")) %>%
  arrange (type, DV)


astx <- ifelse(param_ex$pvalue < (0.05/2), "*", "")

# Export figure

png ("../manuscript_tth/fig2.png", height = 10, width = 20, units = "in", res = 100)
plot(fig_mod)
dev.off()

# Export lavaan table

my_path <- paste0("../manuscript_tth/sm_table1", 
                  "theory",
                  ".docx")

ft <- flextable(param_ex) %>%
  set_caption(caption = " Table 1.Parameter estimates for model theory") %>%
  autofit() 

my_doc <- read_docx()  %>% 
  body_add_flextable(ft)

print (my_doc, target = my_path)
```


# Bayesian latent networks


```{r}
df.bn <- as.data.frame (df3[[1]]) %>%
  mutate (Sex = factor (Sex)) %>%
  mutate (Sensitivity = as.numeric (NA),
          Severity = as.numeric(NA),
          Disability = as.numeric(NA),
          Distress = as.numeric(NA))
```


## Create blacklist

```{r}

#df.bn <- as.data.frame (df3) 

sens.var = grep("PPT", colnames (df.bn), value = TRUE)
severe.var = grep("HDura|HFreq|HInten", colnames (df.bn), value = TRUE)
psych.var = grep("Dep|Anx", colnames (df.bn), value = TRUE)
dis.var = grep("HDI", colnames (df.bn), value = TRUE)
demo.var = grep("Age|Sex|YearsP", colnames (df.bn), value = TRUE)
physiol.var = grep("TrPs", colnames (df.bn), value = TRUE)
others.var = setdiff (names(df.bn), c(demo.var, physiol.var, sens.var, severe.var, dis.var, psych.var))


pair_var <- expand.grid(from = names (df.bn),
                        to = names (df.bn)) %>%
  rownames_to_column()

tiers_keep <- pair_var %>%
  filter (!(grepl (paste0(c(sens.var, severe.var, dis.var, psych.var), collapse = "|"),to))) %>%
  filter (!(grepl (paste0(c(sens.var, severe.var, dis.var, psych.var), collapse = "|"),from))) %>%
  filter (!(grepl (paste0(c(demo.var), collapse = "|"),to))) %>%
  filter (!(grepl ("Disability",from)))


bl <- anti_join(pair_var, tiers_keep, by = "rowname")  %>%
  filter (from != to) %>%
  select (-rowname) %>%
  mutate_all(as.character)

```


## Create whitelist

```{r}

latent1 <- expand.grid(from = "Sensitivity",
                        to = sens.var)
latent2 <- expand.grid(from = "Severity",
                        to = severe.var)
latent3 <- expand.grid(from = "Disability",
                        to = dis.var)
latent4 <- expand.grid(from = "Distress",
                        to = psych.var)

wl <- latent1 %>%
  bind_rows(latent2) %>%
  bind_rows(latent3) %>%
  bind_rows(latent4)
```

## Analysis

```{r, eval = FALSE}

doParallel::registerDoParallel(7)
#n_boot = 200
############
boot  =  foreach (N = 1: 20, .combine='c', .packages = c("tidyverse")) %do% {
  
            foreach (B = 1: 50, .packages = c("tidyverse")) %dopar% {
              set.seed(2345)
  
              df.bn <- data.frame (df3[[N]])
              df.bn <- mutate (df.bn,
                               Sex = factor (Sex),
                               Sensitivity = as.numeric (NA),
                                Severity = as.numeric(NA),
                                Disability = as.numeric(NA),
                                Distress = as.numeric(NA)) 

              boot.sample = df.bn[sample(nrow(df.bn), 
                                                    nrow(df.bn), replace = TRUE), ]
              
              start = bnlearn::bn.fit(bnlearn::empty.graph(names(boot.sample)), boot.sample)
              start$Sensitivity = list(coef = 0, sd = 1)
              start$Severity = list(coef = 0, sd = 1)
              start$Disability = list(coef = 0, sd = 1)
              start$Distress = list(coef = 0, sd = 1)
              
              bnlearn::structural.em(boot.sample, 
                                     start = start,
                                     maximize.args = list(blacklist = bl,
                                                          whitelist = wl))
            }
            
}
#############
doParallel::stopImplicitCluster()  
```

## Set threshold

```{r message=FALSE, warning=FALSE}
set_thres <- seq (0.5, 0.8, 0.01) # try 0.5, 0.6, 0.7. 0.8, the higher to one the sparser the model
bootstr <-  custom.strength(boot, nodes = names(df.bn))

avg_list <- vector ("list", length (set_thres))
deg_list <- vector ("list", length (set_thres))
deg_thres <- vector ("list", length (set_thres))


thres_dag <- function (x) {
  
  if(x[1]>3 & x[2]>3 & x[3]>2 &x[4]>2)
    1 else
      0
  
}

for (n in seq_along(set_thres)) {
  
  avg_list[[n]] <- averaged.network(bootstr, threshold = set_thres[n])
  degs <- map(bnlearn::nodes(avg_list[[n]]), bnlearn::degree, obj =  avg_list[[n]])
  names(degs) <- bnlearn::nodes(avg_list[[n]])
  degs[!grepl(c("Sens|Sever|Dis"), names (degs))] <- NULL
  deg_list[[n]] <- unlist(degs)
  deg_thres[[n]] <- thres_dag(deg_list[[n]])
}

deg <- unlist (deg_thres)

thres <- set_thres[tail(which(deg ==1),1)]
thres

avg <-  averaged.network(bootstr, threshold = 0.5)

g = strength.plot(avg, 
                  bootstr, 
                  shape = "rectangle",
                  main = "Figure")

# graph::nodeRenderInfo(g) = list(fontsize=32)
# renderGraph(g)
```

## BN to SEM 


```{r}
sem_form1 <- "

  # Latent
  Sensitivity =~ PPTcx + PPThx + PPTrm 
  Severity =~ HDura + HFreq + HInten
  Disability =~ HDI_E + HDI_P
  Distress =~ Dep + Anx
  
  # Paths
  Sensitivity ~ Sex
  TrPs ~ Sensitivity + YearsP + Age
  Sleep ~ Sensitivity + Age + Severity
  Distress ~ Severity + Sleep
  Disability ~ YearsP + Age + Sleep + Distress
  
  Disability ~~0*TrPs
"

m1 <- sem.mi (sem_form1, 
           data = df3, 
           orthogonal = TRUE, 
           std.lv = FALSE, 
           auto.fix.first = TRUE, 
           estimator = "MLR",
           se = "robust.huber.white")

summary (m1)

round (fitMeasures(m1, 
            #fit.measures = c("rmsea", "pvalue", "cfi", "tli", "srmr", "nnfi"), 
            test = "D2" , 
            pool.robust = TRUE)[c("rmsea", "pvalue", "cfi", "tli", "srmr", "nnfi")],3)
```


## Plot

```{r}

m1_dummy <- sem (sem_form1, 
                   data = df3[[1]], 
                   std.lv = FALSE, 
                   auto.fix.first = TRUE, 
                   estimator = "MLR",
                   se = "robust.huber.white")

fig <- semPlotModel(m1_dummy )

x = data.frame (summary (m1))
fig@Pars$est <- x$est

fig2 <- drop_nodes(fig, c("HDI_P", "HDI_E", "PPTcx", "PPThx", "PPTrm", "HDura", "HFreq", "HInten", "Dep", "Anx"))

fig2 <- semPaths (fig2, 
          what = "path", 
          whatLabels= "est",
          fixedStyle = c( "white","0"),
          freeStyle = "black",
          residuals = FALSE,
          nCharNodes = 0,
          intercept = TRUE,
          edge.label.cex = 0.8,
          exoCov = FALSE,
          color = list (lat = "grey", man = "white"),
          edge.label.position = 0.5,
          edge.color = "black")

indicator_order  <- c("Sensitivity", "Severity", "Disability", "Distress",
                      "Age", "Sex", "YearsP", "Sleep", "TrPs")

indicator_factor <- c("Sensitivity", "Severity", "Disability", "Distress",
                      "Age", "Sex", "YearsP", "Sleep", "TrPs")

factor_layout <- matrix(c("Sensitivity", NA, "Sleep", NA, "Distress", NA,
                          NA, NA, NA, "Age", NA, "Disability",
                          "Sex",  "TrPs", NA,NA, NA,NA,
                          NA, NA, NA, "YearsP",  NA,"Severity"),
                          byrow = TRUE, 4, 6)

factor_point_to <-  matrix(c( "left", NA, "left", NA, "left",NA,
                          NA, NA, NA, "left", NA,"left",
                          "left", "lefts",NA,  NA, NA,NA,
                          NA, NA, NA, "left",  NA,"left"),
                          byrow = TRUE,4, 6)

fig_mod <- set_sem_layout(fig2, 
                     indicator_order = indicator_order,
                     indicator_factor = indicator_factor,
                     factor_layout = factor_layout,
                     factor_point_to = factor_point_to)
plot(fig_mod)
```


## Montecarlo bootstrap coefficients


```{r}

params <- l2[1: length (coef(m1 ))]

paths <- coef(m1)
names(paths) <- params
var_mat <- vcov(m1)
colnames(var_mat) <- rownames(var_mat) <- params

m1_coef <- monteCarloCI(expr = params,
                           ACM = var_mat,
                           coefs = paths)
m1_coef$paths <- names(coef(m1))


m1_coef <- m1_coef %>%
  filter (!grepl ("~~", paths)) %>%
  separate(paths, into = c("DV", "IV"), sep = "~|=~")
```

## Report

```{r, eval = FALSE}


fixed <- data.frame (DV = c("Sensitivity", "Severity", "Disability", "Distress"),
                     IV = c("PPTcx", "HDura", "HDI_P", "Dep"),
                     Coef = 1,
                     SE = NA,
                     `LB` = NA,
                     `UB` = NA,
                     Pval = NA,
                     Sig = NA)

# Export lavaan table
param_ex<- summary (m1, standardized = TRUE) %>%
  filter (op != "~~") %>%
  rename (DV = lhs,
          IV = rhs,
          Coef = est,
          SE = se,
          Pval = pvalue) %>%
  data.frame () %>%
  inner_join(m1_coef, by = c("DV", "IV")) %>%
  rename (`LB` = ci.lower,
          `UB` = ci.upper) %>%
  mutate_if (is.numeric, round, 3) %>%
  mutate (Sig = ifelse (Pval < 0.05/2, "s", "ns")) %>%
  dplyr::select ( DV, IV, Coef, SE, `LB`, `UB`,Pval, Sig) %>%
  mutate (Coef = as.numeric (Coef))%>%
  bind_rows (fixed)%>%
  mutate (type = ifelse (IV %in% c("PPTcx", "PPThx", "PPTrm", "HDura", "HFreq", "HInten",
                                   "Dep", "Anx", "HDI_P", "HDI_E"), "LV", "Reg")) %>%
  arrange (type, DV)

astx <- ifelse(param_ex$pvalue < (0.05/2), "*", "")


png ("../manuscript_tth/fig3.png", height = 8, width = 15, units = "in", res = 100)
plot(fig_mod)

dev.off()


my_path <- paste0("../manuscript_tth/sm_table2", 
                  "bn",
                  ".docx")

ft <- flextable(param_ex) %>%
  set_caption(caption = " Table 2.Parameter estimates for model BN") %>%
  autofit() 

my_doc <- read_docx()  %>% 
  body_add_flextable(ft)

print (my_doc, target = my_path)
```

# Compare SEM models

```{r}
fitMeasures(m0, fit.measures = c("rmsea", "pvalue", "cfi", "tli", "srmr", "nnfi"))
fitMeasures(m1, fit.measures = c("rmsea", "pvalue", "cfi", "tli", "srmr", "nnfi"))


#vuongtest(m0, m1, adj = "bic")
#icci(m1, m3)

```


# Sensitivity analysis

```{r}

model <- "

  # Latent
  Sensitivity =~ PPTcx + PPThx + PPTrm 
  Severity =~ HDura + HFreq + HInten
  Disability =~ HDI_E + HDI_P
  Distress =~ Dep + Anx
  
  # Paths
  Sensitivity ~ Sex
  TrPs ~ Sensitivity + YearsP + Age
  Sleep ~ Sensitivity + Age + Severity
  Distress ~ Severity + Sleep
  Disability ~ YearsP + Age + Sleep + Distress
  
  Disability ~~0*TrPs
"


sens.model <- "

  # Latent
  Sensitivity =~ PPTcx + PPThx + PPTrm 
  Severity =~ HDura + HFreq + HInten
  Disability =~ HDI_E + HDI_P
  Distress =~ Dep + Anx
  
  # Paths
  Sensitivity ~ Sex
  TrPs ~ Sensitivity + YearsP + Age
  Sleep ~ Sensitivity + Age + Severity
  Distress ~ Severity + Sleep
  Disability ~ YearsP + Age + Sleep + Distress
  
  Disability ~~0*TrPs
  
  Sensitivity ~ phantom1*phantom
  TrPs ~ phantom2*phantom
  Severity ~ phantom3*phantom
  Disability ~ phantom4*phantom
  Distress ~ phantom5*phantom
  YearsP ~ phantom6*phantom
  Sleep ~ phantom7*phantom
  
  phantom =~ 0 # added for mean of zero
  phantom ~~ 1*phantom # added for unit variance
"

my.sa <- sa.aco(data= df3[[1]], 
                model = model, 
                sens.model = sens.model,
                opt.fun = 4, 
                k = 100,
                measurement = TRUE,
                max.iter = 30, 
                seed = 144,
               orthogonal = TRUE, 
               std.lv = FALSE, 
               auto.fix.first = TRUE, 
               estimator = "MLR",
               se = "robust.huber.white")

tables <- sens.tables(my.sa)


tab <- tables$sens.summary %>%
  mutate (change = abs ((mean.est.sens - model.est)/model.est) *100)%>%
  arrange (desc(change))%>%
  mutate_all (round, 3) %>%
  rownames_to_column(var = "path") %>%
  separate (path, c("DV", "IV"), sep = "~") %>%
  select (-model.pvalue) %>%
  rename (`Original coef` = model.est,
          `Mean perturbed coef` = mean.est.sens,
          `Min perturbed coef` = min.est.sens,
          `Max perturbed coef` = max.est.sens,
          `% Change` = change)


my_path <- paste0("../manuscript_tth/sm_table3", 
                  "sens",
                  ".docx")

ft <- flextable(tab) %>%
  set_caption(caption = " Table 2.Parameter estimates for model BN") %>%
  autofit() 

my_doc <- read_docx()  %>% 
  body_add_flextable(ft)

print (my_doc, target = my_path)
```


# Save data

```{r, eval = FALSE}
res <- list (cfa0 = cfa0,
             cfa0_coef = cfa0_coef,
             m0 = m0,
             m0_coef = m0_coef,
             m1 = m1,
             m1_coef = m1_coef,
             df = df,
             dat_imp = dat_imp,
             df3 = df3,
             my.sa = my.sa,
             boot = boot)

saveRDS (res,
         "output/res2.RDS")
```

